Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech

### 2021-03-31 RR_manuscript/Draft_RR.Rmd
:bug: - implement suggested edits, add credit tax

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data. <!-- repetition "data" -->
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g. @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units. <!-- Still not sure why in this example we refer to a lexical contrast when it is clear we are focusing on the segment. Does it make sense to say the acoustic features can differ depending on the position of the consonant in the word? It wouldn't be the same lexical contrast if the segment was in another position... they would be different words and maybe no longer a minimal pair. -->
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
... <!-- what's with the 3 periods? -->

@@

Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models. <!-- It's a technicality but given that bayesian approximation of the posterior is based on sampling, this statement can't be true. I understand you are referring specifically to the MAP and that it would be the same as the MLE point estimate, but this reads as if youre saying the models are equivalent. --> 
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

>>>>

In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by such data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g. @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*

@@

Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e. only the distribution of the data determines the posterior distribution).
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

# Author contributions

<!-- TODO: add LINK to credit -->
See image at link: .

# Conflicts of interest

We have no conflicts of interest to disclose.
